Joint Neighborhood Subgraphs Link Prediction

### 2017-06-30 paper.tex
F

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: a network describing the dispute between 130 countries. A link connecting two nodes (countries) if they dispute. We have 180 links in total in this network. The average degree is 2.5.

@@

We evaluate the performance of employed methods via a 10 splits. Each round, a given ratio of links will be used to train models, and the rest of links are used to test. For \textit{Protein}, \textit{Metabolic}, \textit{Nips} and \textit{Conflict} networks, we set the training ratio to 10$\%$ while the training ratio for \textit{Condmat} and \textit{Powergrid} to 90$\%$. The performance of each method is computed by taking an average of ROC-AUC over 10 rounds.

>>>>

\item \textit{Conflict} \cite{conflict1}, \cite{conflict2}: nodes are countries and edges encode a conflict or a dispute. We have 130 nodes and 180 links in total in this network with a median degree of 2.5.

@@

We evaluate the performance of employed methods splitting 10 times the data in a train and a test part. For \textit{Protein}, \textit{Metabolic}, \textit{Nips} and \textit{Conflict} networks, we use 10$\%$ of the edges to induce the training set while for \textit{Condmat} and \textit{Powergrid} we use 90$\%$ of the links. The performance of each method is computed as the average of the AUC-ROC over the 10 rounds.
